Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-05-14 numerical-mhd-ct.tex
adding dual energy, cosmology, and a better intro

Physically, the divergence of the magnetic field, \Divb, is
identically zero due to the fact that the evolution of the magnetic field is the
curl of a vector, and the divergence of the curl of a vector is identically
zero:
\begin{eqnarray}
\partial \Bvec/\partial t & =& \frac{1}{a} \nabla \times \Evec\\
\Divb & =& 0.
\end{eqnarray}

@@

>>>>

This MHD method was developed by \citet{Collins10} in order to study Population
III stars \citep{Xu08}, molecular clouds \citep{collins12}, and galaxy clusters
\citep{Xu12, Skillman13}.  A full description and suite of test problems can be
found in \citet{Collins10}

The divergence of the magnetic field, \Divb, is
identically zero due to the fact that the evolution of the magnetic field is the
curl of a vector, and the divergence of the curl of a vector is identically
zero:
\begin{eqnarray}
\partial \Bvec/\partial t & =& \frac{1}{a} \nabla \times \Evec\\
\Divb & =& 0.
\end{eqnarray}

@@

Cosmological MHD can be treated in a number of ways.  As described in Section
\red{reference}, the MUSCL with Dedner treats the cosmological dilution of
$\vecB$ with a source term, 
$$ 
\frac{\partial \vecB}{\partial t} - \frac{1}{a}  \nabla \times (\vecv \times
\vecB)  =  -\frac{\dot{a}}{2 a} \vecB. \label{eq:induction_cosmo_source}
$$
However, one can eliminate the right hand side of Equation 
\ref{eq:induction_cosmo_source} by defining
$\vecB^\prime = \vecB / \sqrt{a}.$
Then Equation \ref{eq:induction_cosmo_source} becomes
$$ 
\frac{\partial \vecB^\prime}{\partial t} - \frac{1}{a}  \nabla \times (\vecv \times
\vecB^\prime)  = 0, \label{eq:induction_cosmo_prime_nosource}
$$
and we can reuse each part of the non-cosmological algorithm (hyperbolic solver,
electric field creation, interpolation, projection, and flux correction) without
modification.

Dual energy formalism has also been incorporated in two methods, one internal
energy, similar to that described in Section \ref{sec.hydro.ppm}, and one that
uses entropy.  The additional equations are
\begin{eqnarray}
\end{eqnarray}
\begin{eqnarray}
  \frac{\partial S}{\partial t} +\frac{1}{a} \nabla \cdot (S \vecv) & = &  -
  \frac{ 3 (\gamma - 1) \dot{a}}{a} S \\
  \frac{\partial \rho e}{\partial t} + \frac{1}{a} \nabla \cdot (\rho e \vecv) &
  = & -\frac{ 3(\gamma -1 ) \dot{a}}{a} + \frac{p}{a} \nabla \cdot \vecv,
\end{eqnarray}
where $e$ is the internal energy and $S=p/\rho^{\gamma-1}$ is the entropy.  If
the ratio of thermal to kinetic energy, $\eta$, is below a certain value, the
alternative energy is used.  As in \citet{Li08}, we use $\eta=0.008$.
